### 2021-04-17 Chapter-1/Chapter-1.tex
Updates from Overleaf

\chapter{Introduction} \label{chapter1}
\section{Side-channels}
Side-channel attacks allow an attacker to infer sensitive information based on ``side-channel'' information. Examples of the ``side-channel'' information include execution timing, CPU usages, power consumption, and even sound. For example, in 1996, Kocher demonstrated that an attacker could break cryptosystems like RSA and Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation. The simple modular exponentiation calculates the remainder of an exponent divided by an integer.  The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1. An attacker can infer the whole secret key by measuring the execution time of the operation bit by bit.

When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
\begin{figure}[h]
    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
    \caption{Secret-dependent control-flow transfers}
    \label{fig:secret:cf}
\end{figure}

@@

Various countermeasures have been proposed to defend against side channel attacks. Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new hardware features and changes in modern complex computer systems, which are hard to adopt in reality. Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from code base.

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present relevant backgrounds and related works in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in multiple-trace attack. Chapter~\ref{chapter6} concludes the dissertation.

>>>>

\chapter{Introduction} \label{chapter1}
\section{Side-channels}
A side-channel attack is any attack that allows adversaries to infer sensitive information based on ``side-channel'' information. In 1996, Kocher published the first side-channel attack in the literature. He demonstrated that an attacker could break cryptosystems like RSA or Diffie-Hellman by measuring the execution time of a simple modular exponentiation operation. The simple modular exponentiation calculates the remainder of an exponent divided by an integer.  The simple modular exponentiation operation executes faster when the exponent bit is 0 and slower when the exponent bit is 1. An attacker can infer the whole secret key by measuring the execution time of the operation bit by bit. Since then, researchers have proposed numerous side-channel attacks which exploit numerous kinds of ``side-channel'' information, including execution timing, CPU usages, power consumption,  electromagnetic radiation, and even sound.

Various countermeasures have been proposed to defend against side channel attacks. Hardware-level solutions, such as reducing shared resources, adopting oblivious RAM, and using transnational memory~\cite{203878,217537,shih2017t,Zhang:2015:HDL:2775054.2694372}, need new hardware features and changes in modern complex computer systems, which are hard to adopt in reality. Therefore, a promising and universal direction is software countermeasures, detecting and eliminating side channel vulnerabilities (data flow from secrets to load addresses, and data flow from secrets to branch conditions) from code base. For example, when we examine those side-channel attacks, many of them stem from the two code patterns: \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
\begin{figure}[h]
    \begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
    \caption{Secret-dependent control-flow transfers}
    \label{fig:secret:cf}
\end{figure}

@@

@@

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present relevant backgrounds and related works in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in multiple-trace attack. Chapter~\ref{chapter6} concludes the dissertation and proposes the future work.
